### 2022-08-20 paper/Chapters/Chapter02.tex
update paper update dataset

To solve this problem, some approaches focus on improving the depth map by estimating missing regions. \cite{depth-inpainting-distribution} proposed an approach that considers the depth distributions of neighboring regions to fill the holes in the depth map. \cite{ncnn} uses a deep learning-based approach for painting semi-dense depth maps, which mainly uses the normalized convolution proposed by \cite{nconv}. This approach considers a 0-1 mask to distinguish valid and invalid data points. \cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with an estimated confidence mask. \cite{depth-enhance-guided} also uses a normalized convolution for inpainting the depth map and also uses an RGB image as a guidance.

@@

However, these approaches mainly rely on RGB images as input for estimating the normal or the full depth map. The applied scenarios are mainly indoor scenes such as bedrooms or offices, where the focus is not on the fine details of the object surface, but only on the main directions of each area, such as the directions of the floor, walls, or seats, etc as shown in Figure \ref{fig:dataset-comparison}

>>>>

To solve this problem, some approaches focus on improving the depth map by estimating missing regions. \cite{depth-inpainting-distribution} proposed an approach that considers the depth distributions of neighboring regions to fill the holes in the depth map. \cite{ncnn} uses a deep learning-based approach for painting semi-dense depth maps, which mainly uses the normalized convolution proposed by \cite{nconv}. This approach considers a $ 0-1 $ mask to distinguish valid and invalid data points. \cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with an estimated confidence mask. \cite{depth-enhance-guided} also uses a normalized convolution for inpainting the depth map and also uses an RGB image as a guidance.

@@

However, these approaches mainly rely on RGB images as input for estimating the normal or the fully dense depth map. The applied scenarios are mainly indoor scenes such as bedrooms or offices, where the focus is not on the fine details of the object surface, but only on the main directions of each area, such as the directions of the floor, walls, or seats, etc as shown in Figure \ref{fig:dataset-comparison}
